---
title: "Homework1-Week4"
author: "Silvy van Kuijk"
date: "September 27, 2016"
output: html_document

---

###<span style="color:green">Homework - Problem 1</span>

Every Saturday, at the same time, a primatologist goes and sits in the forest in the morning and listens for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number calls she will hear in that time is exactly 15. Let $X$ represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

###What is the probability that she will hear more than 8 calls during any given session?

As this is a count, I'm assuming I'll need to use the Poisson Distribution functions.

```{r}
duet.prob <- 1 - ppois(q=8, lambda=15) #Note to self: the ppois function does 8 or less, so therefore you need to do 1 - ppois!
duet.prob
```

###What is the probability that she will hear no calls in a session?

```{r}
song.prob <- dpois(x=0, lambda=15)
song.prob
```

###What is the probability that she will hear exactly 3 calls in a session?

```{r}
call.prob <- dpois(x=3, lambda=15)
call.prob
```

###Plot the relevant Poisson mass function over the values in range 0 ≤ $x$ ≤ 30.

```{r}
#Note to self: see page 340 of 'The Book of R' for more info about this mass function!
duet.plot <- barplot(dpois(x=0:30, lambda=15), space=0, ylab="Frequency", xlab="Count", names.arg=0:30)
duet.plot
```

###Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
#Note to self: See page 341 of 'The Book of R'.
two.years <- rpois(n=104, lambda=15)
```

###Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
hist(two.years, xlim=c(0,30), ylab="Frequency", xlab="Count", main="Two years of Saturday morning sessions")
```

**Comparison:** Even though the two plots both show a peak at 15 calls, the second plot is not normally distributed, but skewed to the right. She seems to have no days at which she records 0-6 calls. (Guess she was definitely not studying _~~Callicebus~~ Plecturocebus discolor_ then...)

<span style="color:red">Okay, this explanation above may not really make sense, because every time I knit again, the histogram looks different. (Not surprising, because it probably re-runs the simulation again each time I knit!</span>
